\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

% ================= Header =================
\begin{center}
    {\Huge \textbf{Ahmed Hassan Eldemery}} \\ \vspace{2mm}
    {\Large AI Engineer | Machine Learning Engineer} \\ \vspace{2mm}
    Mansoura, Egypt | +201094670920 | \href{mailto:ahmedeldemery68@gmail.com}{ahmedeldemery68@gmail.com} \\ \vspace{1mm}
    \href{https://www.linkedin.com/in/ahmed-eldemery-a210aa306/}{LinkedIn} |
    \href{https://github.com/Demro7}{GitHub} |
    \href{https://www.kaggle.com/ahmedeldemery}{Kaggle}
\end{center}

% ================= Summary =================
\section{Professional Summary}
AI Engineer and Machine Learning professional specializing in end-to-end ML pipelines, LLM-powered applications, and intelligent automation systems. Skilled in backend API development, computer vision, and prompt engineering using Python, FastAPI, Scikit-learn, OpenCV, and MongoDB. Currently building production-grade systems for multimodal AI classification and business automation at Try GC, delivering measurable impact on real-world operational challenges.
% ================= Education =================
\section{Education}
\textbf{Bachelor of Computer Science (Minor in Artificial Intelligence)} \hfill Oct 2023 -- July 2027 (Expected) \\
\textit{Mansoura University} \hfill Mansoura, Egypt
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item \textbf{Relevant Coursework:} Linear Algebra, Probability \& Statistics, Data Structures, Machine Learning, Computer Vision
\end{itemize}

% ================= Skills =================
\section{Technical Skills}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item \textbf{AI \& LLMs:} LLM Integration, Prompt Engineering, LangChain, RAG, Generative AI, Groq API, Llama 3, OpenAI API
    \item \textbf{Machine Learning:} Scikit-learn, XGBoost, Regression, Classification, Clustering, Feature Engineering
    \item \textbf{Computer Vision \& Speech:} OpenCV, YOLOv8, PaddleOCR, MediaPipe, TalkNet, Whisper, CLIP
    \item \textbf{Data \& Visualization:} Pandas, NumPy, Matplotlib, Seaborn, Exploratory Data Analysis (EDA)
    \item \textbf{Backend \& Frontend:} FastAPI, Flask, React, REST APIs, WebSockets, JWT Authentication, PGVector, Qdrant
    \item \textbf{Tools \& Architecture:} Python, SQL, Git, Docker, Docker Compose, Microservices, Chrome Extensions (MV3)
\end{itemize}

% ================= Experience =================
\section{Professional Experience}

\textbf{AI Specialist} \hfill Apr 2026 -- Present \\
\textit{Try GC (Formerly Grand Community)} \hfill On Site
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Built a multimodal influencer classification system processing \textbf{60,000+ profiles}, combining computer vision (face/video analysis) and speech models (TalkNet, Whisper) to auto-classify creators.
    \item Developed a Manifest V3 Chrome Extension and FastAPI backend to record meetings, transcribe Arabic conversations via Whisper, and extract structured marketing insights using Llama-3.3 via Groq.
    \item Designed LLM integration pipelines and prompt workflows, reducing manual operational efforts across the company's core database.
\end{itemize}

\vspace{2mm}

\textbf{Machine Learning Engineer Trainee} \hfill June 2025 -- Dec 2025 \\
\textit{Huawei \& Mansoura University Collaboration} \hfill Mansoura, Egypt
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Engineered end-to-end ML pipelines (Python, Scikit-learn), improving model accuracy by $\sim$12\% via feature engineering.
    \item Trained and evaluated supervised and unsupervised models on real-world datasets.
\end{itemize}

\vspace{2mm}

\textbf{Machine Learning Engineer Intern} \hfill July 2025 -- Aug 2025 \\
\textit{National Telecommunication Institute (NTI)} \hfill Mansoura, Egypt
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Developed a predictive analytics model using Scikit-learn to forecast e-commerce customer spending behavior.
    \item Executed end-to-end ML data pipelines, enabling data-driven insights from historical sales data.
\end{itemize}

% ================= Projects =================
\section{Key Projects}

\textbf{\href{https://github.com/Demro7/influencer-video-classifier}{Influencer Video Classifier (Try GC)}} \hfill \textit{Python, OpenCV, TalkNet, Whisper}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Engineered a scalable production pipeline combining computer vision with speech models to classify creators based on content type and speaking style.
    \item Automated marketing operations by fully replacing manual classification workflows across a massive database.
\end{itemize}

\vspace{1mm}

\textbf{\href{https://github.com/Demro7/ai-meeting-assistant}{AI Meeting Assistant (Try GC)}} \hfill \textit{FastAPI, Chrome Extension (MV3), Groq API, Whisper}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Engineered a Manifest V3 Chrome Extension utilizing offscreen documents to bypass service worker constraints for real-time audio mixing and secure microphone capture.
    \item Built a stateless FastAPI backend with strict Pydantic validation to process audio chunks via Groq's Whisper-large-v3 and extract structured Arabic marketing insights using Llama-3.3 in JSON mode.
\end{itemize}

\vspace{1mm}

\textbf{\href{https://github.com/Demro7/VoltIQ-}{VoltIQ — Smart Electricity Platform}} \hfill \textit{FastAPI, Flask, YOLOv8, PaddleOCR, XGBoost, PGVector, Docker}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Architected a microservices AI platform combining computer vision OCR, predictive ML, and a RAG document assistant.
    \item Built an OpenCV/PaddleOCR pipeline to read LCD 7-segment displays and trained XGBoost models for anomaly detection and balance depletion forecasting.
    \item Deployed a FastAPI RAG microservice utilizing PGVector/Qdrant and LLMs (Gemini/OpenAI) for context-grounded Q\&A.
\end{itemize}

\vspace{1mm}

\textbf{\href{https://github.com/Demro7/YAQIZ}{YAQIZ — AI Workplace Safety \& Fatigue Monitoring}} \hfill \textit{FastAPI, React, YOLOv8, MediaPipe, Docker}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Built a full-stack platform combining YOLOv8 PPE detection with ByteTrack worker tracking and MediaPipe fatigue analysis.
    \item Engineered WebSocket pipelines for live video streaming and containerized the full stack using Docker for scalable deployment.
\end{itemize}

\vspace{1mm}

\textbf{\href{https://github.com/Demro7/Digital-Employee}{Digital Employee – AI MSME Sales Assistant}} \hfill \textit{Python, Flask, OpenAI API, MongoDB, JWT}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Built a bilingual LLM chat assistant converting conversations into structured orders with auto-generated IDs.
    \item Implemented role-based access, low-stock alerts, and config-driven workflows for 10+ business sectors.
\end{itemize}

\vspace{1mm}

\textbf{\href{https://github.com/magedyasse/ErgoAi}{ErgoAI – Intelligent Health \& Productivity Assistant}} \hfill \textit{Python, OpenCV, Computer Vision}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Developed an AI-powered desktop app utilizing OpenCV to detect blink rate, yawning, and posture at $\sim$20 FPS.
    \item Achieved \textbf{3rd Place} in the Computer Vision Course (Mansoura University) and \textbf{3rd Place} at the Ibtikar 8 Innovation Competition.
\end{itemize}

\vspace{1mm}

\textbf{Data \& Academic Projects} \hfill \textit{Scikit-learn, GMM, Pandas}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Developed predictive E-commerce spending models, USA Adult Income EDA, and unsupervised GMM Image Segmentation pipelines.
\end{itemize}

% ================= Hackathons =================
\section{Hackathons \& Competitions}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item \textbf{Huawei Developer Competition (Northern Africa):} Advanced to Top 50 teams (Team Sanad) presenting an AI-driven solution in a regional competitive environment (2025).
    \item \textbf{First AI Summit Week Hackathon (Mansoura Univ):} Developed and exhibited the initial prototype of the Digital Employee Assistant alongside teams from 16 universities (2026).
    \item \textbf{Egypt Hackathon 4.0 (GDG Delta):} Built the initial prototype of YAQIZ in a highly competitive hackathon among 120+ teams and 600+ developers (2025).
\end{itemize}

% ================= Honors =================
\section{Honors \& Certificates}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item \textbf{Awards:} 3rd Place – Ibtikar 8 Innovation Comp (2025) | 2nd Place – AI Course Comp (Apr 2025) | Digitopia Semi-Finalist (June 2025).
    \item \textbf{ALX Africa Data Science Program:} 15-month intensive track in Data Analytics and Machine Learning (June 2026).
    \item \textbf{Certifications:} NVIDIA (Building LLM Applications, AI for All) | Intro to Machine Learning (Grade: Excellent) | Applied Data Science \& Python.
\end{itemize}

\end{document}